---
title: "p8105_hw4_p1_pups_data"
author: "Yulan Zhang, Xiangyu Shi"
date: "October 30, 2017"
output: html_document
---

```{r load library, message = FALSE}
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(ggridges)
```
Problem 1


```{r load tidy data}
pups_data = read_csv("./data/FAS_pups.csv",
  col_types = "ciiiii") %>%
  clean_names() %>%
  gather(key = outcome, value = post_natal_days, pd_ears:pd_walk) %>%
  mutate(
    outcome = str_replace(outcome, "pd_", "")
    ) %>%
  filter(post_natal_days != "NA")
```

```{r make the plot}

pups_data %>% 
  mutate(outcome = fct_reorder(outcome, post_natal_days)) %>%
  ggplot(aes(y = outcome, x = post_natal_days, color = outcome, fill = outcome) ) +
  geom_density_ridges(bandwidth = 0.25) +
  labs(
    title = "distribution of post-natal days for each developmental landmark",
    x = "Post-natal Days",
    y = "Developmental Landmark",
    caption = "distribution of post-natal days for each developmental landmark"
  )
?geom_density_ridges
```


The plot illustrates the distribution of post-natal days for each developmental landmark. We observe that the four outcomes of interest, ears, pivot, walk and eyes develop from 2 days to 15 days post-natal: 

- Ear development is mostly distributed at 4 days post-natal.
- Pivot development has a wide distribution from 4 days to 9 days post-natal.
- Walk development also has a wide distribution but ranges from 6 days to 14 days post-natal.
- Lastly eye development is mostly seen at 13 days post-natal.




